Staged Abstract Interpreters

### 2019-09-07 paper/10_intro.tex
intro

Roughly at the same time when abstract interpretation was proposed in the
1970s, \citet{futamura1971partial} observed a close
connection between interpreters and compilers through a hierarchy of
specializations, since then known as Futamura Projections. The first Futamura
projection describes that specializing an interpreter to the input program
removes interpretative overhead and yields an equivalent executable
that runs faster. 
In recent years, the idea of Futamura projections has gained more attentions
and has been successfully applied to many real-world problems, examples including
query compilers \cite{DBLP:conf/sigmod/TahboubER18}, PyPy \cite{Bolz:2009:TMP:1565824.1565827},
Truffle \cite{Marr:2015:TVP:2814270.2814275}, etc.
The challenge here: can we apply the same idea to a general abstract interpreter
to make it run faster? The solution is not obvious, as we need to specialize
a nonstandard semantics that extensively uses nondeterminism, operates on
abstract domains, and computes fixed-points iteratively over caches.

>>>>

Roughly at the same time when abstract interpretation was proposed,
\citet{futamura1971partial} observed a close
connection between interpreters and compilers through a hierarchy of
specializations, since then known as Futamura Projections. The first Futamura
projection describes that specializing an interpreter to the input program
removes interpretative overhead and yields an equivalent executable
that runs faster. 
In recent years, the idea of Futamura projections has attracted more attentions
and has been successfully applied to many real-world problems, including
query compilers \cite{DBLP:conf/sigmod/TahboubER18}, PyPy \cite{Bolz:2009:TMP:1565824.1565827},
Truffle \cite{Marr:2015:TVP:2814270.2814275}, etc.
The challenge here: can we apply Futamura projections to a general abstract interpreter
to make it run faster? The solution is not obvious, as we need to specialize
a nonstandard semantics that extensively uses nondeterminism, operates on
abstract domains, and computes fixed-points iteratively over caches.
